---
title: "Describing Returns"
author: "Mike Aguilar"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---
```{css, echo=FALSE}
.scroll-200 {
  max-height: 200px;
  overflow-y: auto;
  background-color: inherit;
}
```

```{r, include=TRUE, echo = FALSE}
knitr::opts_chunk$set(fig.width=10,echo=TRUE, warning=FALSE, message=FALSE, class.output="scroll-200")
```

<!-- ## Describing Returns -->

### Mean of Returns
```{r child = 'MeanofReturns.Rmd'}
```


### Var.& Std.Dev. of Returns
```{r child = 'Var&StdDevofReturns.Rmd'}
```


### Skew & Kurt. of Returns
```{r child = 'SkewnessandKurtosisofReturns.Rmd'}
```


### Min/Max of Returns
```{r child = 'MinMaxofReturns.Rmd'}
```


### Sample Statistics
```{r child = 'SampleStatistics.Rmd'}
```
 

### Histogram
```{r child = 'Histogram.Rmd'}
```


### Hist. with Density Overlay
```{r child = 'HistogramwithDensityOverlay.Rmd'}
```


### Histogram with VaR
```{r child = 'HistogramwithVaR.Rmd'}
```



### Hist. with Risk Boundaries
```{r child = 'HistogramwithRiskBoundaries.Rmd'}
```


### Relative Freq. Hist.
```{r child = 'RelativeFrequencyHistogram.Rmd'}
```


### Order Rank
We can rank returns from big to small. The highest (or most favorable) return rank is 1 and the lowest (or least favorable) return rank is 252 in our example.
```{r child = 'OrderRank.Rmd'}
```


### Quantiles Historical Ret.
Quantile determines how many values in a distribution are above or below a certain limit, so it is important for performance analysis.
```{r child = 'QuantilesofHistoricalReturns.Rmd'}
```


### Find Date of Quantile
What is the date of the 80th percentile observation?
```{r child = 'FindDateofSpecificQuantile.Rmd'}
```


### Percentile of Obs. on Date
What is the percentile of the observation on Mar.10, 2020?
```{r child = 'PercentileofObsonSpecificDate.Rmd'}
```


### Visualize Outliers
This is a simple heuristic, not a formal rule.  Your initial EDA can control the threshold you choose to set. 
```{r child = 'VisualizeOutliers.Rmd'}
```


### Boxplot of Outliers
The observations in red are potential outliers since they lie >75th quantile and less than 25th quantile. 
```{r child = 'BoxplotofOutliers.Rmd'}
```


### Compute Z Scores
```{r child = 'ComputeZScores.Rmd'}
```

### DeMean 
```{r child = 'DeMean.Rmd'}
```

### ReScale 
```{r child = 'ReScale.Rmd'}
```

### Compute IQR
```{r child = 'ComputeIQR.Rmd'}
```


### Drop Outliers
```{r child = 'DropOutliers.Rmd'}
```


### Replace Outliers with Mean
```{r child = 'ReplaceOutlierswithMean.Rmd'}
```


### Replace Outliers with Quant.
```{r child = 'ReplaceOutlierswithExtremeQuantiles.Rmd'}
```
Notice that the min and max are equal to Q1 and Q3, respectively, confirming that we've trimmed appropriately. 


### Rolling Mean Return
```{r child = 'RollingMeanReturnover250-days.Rmd'}
```


### Rolling Std of Returns
```{r child = 'Rolling250-dayStdofReturns.Rmd'}
```


### Rolling Skewness of Returns
```{r child = 'Rolling250-daySkewofReturns.Rmd'}
```


### Rolling Kurtosis of Returns
```{r child = 'Rolling250-dayKurtosisofReturns.Rmd'}
```

### Rolling Total Return
```{r child = 'Rolling250-dayTotalReturn.Rmd'}
```

### Create Calendar Dummies
```{r child = 'CreateCalendarDummy.Rmd'}
```

### Create Dummies by Value
```{r child = 'CreateValueDummy.Rmd'}
```

### Test Equal Mean Returns
```{r child = 'EqualMeans.Rmd'}
```

### Test Mean Ret. One-Sided
```{r child = 'EqualMeansOneSided.Rmd'}
```

### Test Equal Variance Returns
```{r child = 'EqualVariance.Rmd'}
```

### Return Correlation
```{r child = 'ReturnCorrelation.Rmd'}
```


### Visualize Correlations (v1)
```{r child = 'VisualizeCorrelations.Rmd'}
```


### Visualize Correlations (v2)
The `corrplot()` function from package \textbf{corrplot} allows to draw other fancy correlation graphs(go for this notebook for more examples)
```{r child = 'VisualizeCorrelations(V2).Rmd'}
```


### Rolling Correlations
```{r child = 'RollingCorrelations.Rmd'}
```


### Covariance of Returns
```{r child = 'CovarianceofReturns.Rmd'}
```



<!-- ### PDF for Multiple Assets -->


<!-- ### CDF for Multiple Assets -->



