---
title: "SARIMA"
author: "Mike Aguilar"
date: "3/30/2022"
output: html_document
---


A seasonal autoregressive integrated moving average (SARIMA) model is one step different from an ARIMA model based on the concept of seasonal trends.

#### Fit SARIMA Giving Model Orders
```{r}
rm(list=ls()) # clear workspace
cat("\014")  # clear console
library(Quandl)
Quandl_key = read.csv("quandlkey.csv",stringsAsFactors=FALSE)$Key
Quandl.api_key(Quandl_key)
startd<-"2000-01-01"
endd<-"2018-01-01"
ticker <- "FRED/HOUSTNSA" #New Privately-Owned Housing Units Started: Total Units
HSNG <- Quandl(ticker, type="ts",start_date=startd, end_date=endd)
{plot(HSNG) 
abline(v = ts(c(2000,2005,2010,2015)),col = "red") # v is for vertical lines
abline(v = ts(c(2001,2002,2003,2004)), col = "blue", lty = 2)}
# Evidence of seasonality

### Decide the order of SARIMA
library(astsa)
acf2(HSNG, 48) # Interpret: The slow decay shown in the ACF is a sign that differencing may be required
acf2(diff(HSNG), 48) # Interpret: Even with the first order of differencing, we observe that there is still slow decay in the ACF plots at a seasonal lag period of 12. This thus suggest a seasonal difference to be applied.

acf2(diff(diff(HSNG),12),48)
# Interpret: 
# Seasonal Order: From the seasonal lag perspective, we can see that the ACF cuts off at the 2nd seasonal lag, while the PACF appears to tail off. This would suggest a SARMA model of (0,2). 
# ARMA Order: Within the first seasonal cycle, it can be seen that the ACF appears to be cutting off at lag = 1, while PACF appears to be cutting off at lag = 3. 
# Thus a proposed model can be ARMA (3,1) x Seasonal (0,3)(lag = 12) for the differenced time series. 


### Fit SARIMA Model
arima(HSNG, order = c(3,1,1), seasonal = list(order = c(0,1,2), period = 12))

library(forecast)
sarima(HSNG, p=3, d=1, q=1, P=0, D=1, Q=2, S=12) # sarima() takes in arguments in the following order: data, ARIMA inputs (p,d,q), SARIMA inputs (P,D,Q), and seasonal lag S 


### Forecast
sarima.for(HSNG, n.ahead = 20, p=3, d=1, q=1, P=0, D=1, Q=2, S=12) # forecast prediction for next 20 time points
```


#### Fit SARIMA Without Giving Model Orders
We can use the `auto.arima()` function from the `forecast` package and set `seasonal = TRUE` to ask R to return the best ARIMA/SARIMA model according to either AIC, AICc or BIC value.  
```{r}
rm(list=ls()) # clear workspace
cat("\014")  # clear console
library(Quandl)
Quandl_key = read.csv("quandlkey.csv",stringsAsFactors=FALSE)$Key
Quandl.api_key(Quandl_key)
startd<-"2000-01-01"
endd<-"2018-01-01"
ticker <- "FRED/HOUSTNSA" #New Privately-Owned Housing Units Started: Total Units
HSNG <- Quandl(ticker, type="ts",start_date=startd, end_date=endd)
{plot(HSNG) 
abline(v = ts(c(2000,2005,2010,2015)),col = "red") # v is for vertical lines
abline(v = ts(c(2001,2002,2003,2004)), col = "blue", lty = 2)}
# Evidence of seasonality


### Fit SARIMA Model
library(forecast)
auto.arima(HSNG, seasonal = TRUE)
# We have a model with ARIMA order (p=1,d=1,q=1), seasonal order (P=0,D=1,Q=2), and seasonal lag S=12
```