---
title: "Optimal Portfolios"
author: "Mike Aguilar"
output: 
  html_document:
    mode: selfcontained
    toc: true
    toc_float: true
    number_sections: no
    toc_depth: 3
---
```{css, echo=FALSE}
.scroll-200 {
  max-height: 200px;
  overflow-y: auto;
  background-color: inherit;
}
```

```{r, include=TRUE, echo = FALSE}
knitr::opts_chunk$set(fig.width=10,echo=TRUE, warning=FALSE, message=FALSE, class.output="scroll-200")
```




### Min Variance-Long Only
Minimum Variance, Subject to Target Return, Fully Invested, Long Only 
```{r child = 'MinVariance-TargetReturnFullyInvestedLongOnly.Rmd'}
```

### Min Variance-Long/Short
```{r child = 'MinVariance-TargetReturnFullyInvestedLongShort.Rmd'}
```


### Max Sharpe-LongOnly
```{r child = 'MaxSR-LongOnly.Rmd'}
```

### Max Sharpe-Long/Short
```{r child = 'MaxSR-LongShort.Rmd'}
```


### Max Sharpe-Weight Bounds
```{r child = 'MaxSR-BoxConstraint.Rmd'}
```


### Max Sharpe-Limit #Positions
```{r child = 'MaxSR-NumberPositions.Rmd'}
```


### Max Sharpe-FactorExposure
```{r child = 'MaxSharpe-FactorExposureConstraint.Rmd'}
```

### Max Sharpe-Transaction
```{r child = "MaxSharpe-TransactionCostConstraint.Rmd"}
```


### Max Sharpe-Reoptimizing 
```{r child = 'MaxSharpe-FullyInvestedLongShortRebal.Rmd'}
```


### Max Utility
```{r child = 'MaxUtility-FullyInvestedLongShort.Rmd'}
```


### Efficient Frontier 
```{r child = 'EfficientFrontier.Rmd'}
```

### Fwd Looking Min Variance
```{r child = 'ForwardLookingOptimMinVar.Rmd'}
```

### Fwd Looking Max Sharpe
```{r child = 'ForwardLookingOptimMaxSR.Rmd'}
```

