---
title: "Regression"
author: "Mike Aguilar"
output: 
  html_document:
    mode: selfcontained
    toc: true
    toc_float: true
    number_sections: no
    toc_depth: 3

---
```{css, echo=FALSE}
.scroll-200 {
  max-height: 200px;
  overflow-y: auto;
  background-color: inherit;
}
```

```{r, include=TRUE, echo = FALSE}
knitr::opts_chunk$set(fig.width=10,echo=TRUE, warning=FALSE, message=FALSE, class.output="scroll-200")
```

### Univariate Regression
```{r child = 'UnivariateRegression.Rmd'}
```

### Multivariate Regression
```{r child = 'MultivariateRegression.Rmd'}
```

### Regress w/Interactions
```{r child = 'Interactions.Rmd'}
```

### Regress w/Calendar Dummy
```{r child = 'RegressionCalendarDummy.Rmd'}
```


### Regression Plots
```{r child = 'RegressionPlots.Rmd'}
```

### Regression Plots(v2)
```{r child = 'RegressionPlotsV2.Rmd'}
```

### Extract Regress. Coef. 
```{r child = 'ExtractRegCoefficients.Rmd'}
```

### Extract Regression Residuals
```{r child = 'ExtractRegResiduals.Rmd'}
```

### Regression Fitted Values
```{r child = 'ExtraRegFitted.Rmd'}
```

### Regression Predictions
```{r child = 'RegressionPredict.Rmd'}
```

### Test Parameter Significance
```{r child = 'TestParameters.Rmd'}
```

### Test Param. Sig. One-sided
```{r child = 'TestParametersOneSided.Rmd'}
```

### Test Joint Hypothesis
```{r child = 'JointHypTest.Rmd'}
```

### Test Joint Hyp. Wald
```{r child = 'WaldTest.Rmd'}
```

### Variance Infl. Factor
```{r child = 'VarInfFactor.Rmd'}
```

### BPTest-Heteroscedasticity
```{r child = 'BPTest.Rmd'}
```

### White StdErr. Hetero.
```{r child = 'WhiteStdErrors.Rmd'}
```

### Hetero.Robust T-Test
```{r child = 'RobustTTest.Rmd'}
```

### Hetero.Robust Wald Test
```{r child = 'HeteroRobustWaldTest.Rmd'}
```

### Test for serial correlation
```{r child = 'DWTest.Rmd'}
```

### Test for serial correlation 2
```{r child = 'BGTest.Rmd'}
```

### Test for serial correlation 3
```{r child = 'LBTest.Rmd'}
```

### Fixing Serial correlation
```{r child = 'NeweyWest.Rmd'}
```
